Holomorphic field theories and higher algebra

### 2024-09-17 draft.tex
i am writing in stereo
pert def has had a full pass

\brian{Comparison}

@@

As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
(For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it's due to the original notation people used.}
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformatino quantization); 
the relevant moduli space being the derived mapping space between complex manifolds.

@@

\begin{dfn}
A {\em local cyclic structure} on a holomorphic local Lie algebra is a degree $-3$ map
\[
\langle -,-\rangle: V \otimes V \to K_X
\]
of holomorphic vector bundles\footnote{Here $\otimes$ denotes the Whitney tensor product of vector bundles on $X$.} such that 
\begin{itemize}
\item if $f, g$ are holomorphic sections of $V$, then 
\[
\langle Q^{hol}f, g \rangle + (-1)^{|f|} \langle f, Q^{hol} g \rangle = 0
\]
so that the pairing is a cochain map, and
\item if $f, g, h$ are holomorphic sections of $V$, then 
\[
\langle f, [g,h] \rangle = (-1)^{|f|} \langle h,  \rangle
\]
so that the pairing is invariant for the bracket.
\end{itemize}
\owen{We must check the signs. Am I missing something.}
\end{dfn}

Given a local cyclic structure, there is an action functional
\[
\int_X \frac{1}{2} \langle f, \dbar f + Q^{hol} f \rangle + \frac{1}{3!} \langle f, [f,f] \rangle 
\]
whose equation of motion is the Maurer-Cartan equation
\[
\dbar f + Q^{hol}f + \frac{1}{2} [f,f] = 0.
\]

>>>>

@@

As a more mundane example, let $\RR\Hol(X,Y)$ denote the derived moduli space of holomorphic maps from some complex manifold $X$ to another complex manifold $Y$.
(For $Y = V$ a vector space, a ``derived'' enhancement is familiar as the higher dimensional cohomology $H^*(X, \cO) \otimes V$.)
In derived geometry one can take a ``shifted cotangent bundle'' $T^*[-1] \RR\Hol(X,V)$,
and this derived moduli space encodes solutions to
a field theory known as the $\beta\gamma$ system with target~$V$.\footnote{The name is silly: it's due to the original notation people used.}
Every question one asks about the classical physics of the $\beta\gamma$ theory translates into a question about this moduli space.
Other classes of examples are afforded by holomorphic variants of the AKSZ $\sigma$-models (such as the Poisson $\sigma$-model that appears in Kontsevich's construction of deformation quantization); 
the relevant moduli space being the derived mapping space between complex manifolds.

@@

\begin{dfn}
A {\em local cyclic structure} on a holomorphic local Lie algebra is a degree $-3$ map
\[
\langle -,-\rangle: V \otimes V \to K_X
\]
of holomorphic vector bundles\footnote{Here $\otimes$ denotes the Whitney tensor product of vector bundles on $X$.} such that 
\begin{itemize}
\item if $f, g$ are holomorphic sections of $V$, then 
\[
\langle Q^{hol}f, g \rangle + (-1)^{|f|} \langle f, Q^{hol} g \rangle = 0
\]
so that the pairing is a cochain map, and
\item if $f, g, h$ are holomorphic sections of $V$, then 
\[
\langle f, [g,h] \rangle = (-1)^{|f|} \langle h,  \rangle
\]
so that the pairing is invariant for the bracket.
\end{itemize}
\owen{We must check the signs. And am I missing anything?}
\end{dfn}

Given a local cyclic structure, there is an action functional
\[
\int_X \frac{1}{2} \langle f, \dbar f + Q^{hol} f \rangle + \frac{1}{3!} \langle f, [f,f] \rangle 
\]
whose equation of motion is the Maurer-Cartan equation
\[
\dbar f + Q^{hol}f + \frac{1}{2} [f,f] = 0.
\]
Thus a holomorphic local Lie algebra with a local cyclic structure models a perturbative holomorphic field theory.

The reader might notice that such Maurer-Cartan equations only ever involve quadratic and linear terms in the field.
To incorporate cubic and higher terms in the equations of motion,
one should define holomorphic local $L_\infty$ algebras and local cyclic structures,
which are a modest and straightforward generalization, if one knows what $L_\infty$ algebra means.
Such definitions can be found in~\cite{CG2}.
